Renewal and stability in populations structured by remaining years of life

### 2016-11-30 ThanoRepro/ThanoRepro.tex
still in midst of edits pre thano renewal

%\setlength\PreviewBorder{5pt}
\usepackage{natbib}
\bibpunct{(}{)}{,}{a}{}{;} 
\usepackage{url}
\usepackage{nth}
% for the d in integrals
\newcommand{\dd}{\; \mathrm{d}}
\newcommand{\ec}{\quad\quad\text{,}}
\newcommand{\ep}{\quad\quad\text{.}}
\defcitealias{HMD}{HMD}
\usepackage[top=2in, bottom=1.5in, left=1in, right=1in]{geometry}
\usepackage{setspace}
\doublespacing

@@

Remaining lifetime is different in this respect because we do not know when we
will die--- it is only knowable retrospectively or probabilistically. Under a set of simple assumptions, the same lifetable used to
estimate $\ell(a)$ can be used to
partition and recombine counts observed by age into estimates
classified by years of life left. Our objective is then to estimate a population
structure component, similar to $\ell(a)e^{-ra}$, and a fertility component
similar to $m(a)$, but each for the years left case. Taken together, these
componenents yield the years left renewal model.

>>>>

%\setlength\PreviewBorder{5pt}
\usepackage{natbib}
\bibpunct{(}{)}{,}{a}{}{;} 
\usepackage{url}
\usepackage{nth}
% for the d in integrals
\newcommand{\dd}{\; \mathrm{d}}
\newcommand{\ec}{\quad\quad\text{,}}
\newcommand{\ep}{\quad\quad\text{.}}
\defcitealias{HMD}{HMD}
\usepackage[top=2in, bottom=1.5in, left=1in, right=1in]{geometry}
\usepackage{setspace}
%\doublespacing

@@

Fertility rates by remaining lifetime is different in this respect because death
dates can not be registered on birth certificates in the way that
maternal age or birth year can; Death timing is only knowable retrospectively or probabilistically. Since
it is difficult to imagine what a fertility schedule might look like when
classified by remaining years of life, I give two examples, first of empirically
tabulated years-left female fertiltiy rates, and second rates derived
probabilistically using a lifetable. Empirical years-left fertility rates refer
to the

 Under
a set of simple assumptions, the same lifetable used to estimate $\ell(a)$ can be used to partition and recombine counts observed by age into estimates classified by years of life left. Our objective is then to estimate a population structure component, similar to $\ell(a)e^{-ra}$, and a fertility component
similar to $m(a)$, but each for the years left case. Taken together, these
componenents yield the years left renewal model.
